%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{abhijeet_viswa-deedy-resume-openfont}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Abhijeet}{Viswakumar}{
\href{mailto:abhijeetviswa@gmail.com}{abhijeetviswa@gmail.com} | \href{mailto:f20181032@hyderbad.bits-pilani.ac.in}{f20181032@hyderbad.bits-pilani.ac.in} | +91 807 820 4438}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.25\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education}

\subsection{BITS Pilani}
\descript{B.E. Electronics and Instrumentation Engineering}
\location{July 2022 | Hyderabad, India}
\location{Current CGPA: \normalfont \textbf{7.76/10}}
\subsectionsep

\subsection{Amrita Vidyalayam}
\descript{CBSE Class XII, 95.8\%}
\location{March 2017 | Palakkad, India}
\subsectionsep

\subsection{Amrita Vidyalayam}
\descript{CBSE Class X, 10 GPA}
\location{March 2015 | Palakkad, India}
\secondarysectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{Coursework}
% \subsection{Graduate}
% Advanced Machine Learning \\
% Open Source Software Engineering \\
% Advanced Interactive Graphics \\
% Compilers + Practicum \\
% Cloud Computing \\
% Evolutionary Computation \\
% Defending Computer Networks \\
% Machine Learning \\
% \sectionsep
%
% \subsection{Undergraduate}
% Information Retrieval \\
% Operating Systems \\
% Artificial Intelligence + Practicum \\
% Functional Programming \\
% Computer Graphics + Practicum \\
% {\footnotesize \textit{\textbf{(Research Asst. \& Teaching Asst 2x) }}} \\
% Unix Tools and Scripting \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\itemlabel{Proficient}
\begin{itemize*}
 \item Python
 \item Java
 \item Kotlin
 \item PHP
 \item SQL
\end{itemize*}
\subsectionsep

\itemlabel{Familiar}
\begin{itemize*}
 \item C
 \item C++
\end{itemize*}
\subsectionsep

\subsection{Tools \& Technologies}
\begin{itemize*}
 \item Django
 \item Android
 \item Git
 \item Docker
 \item REST
 \item Postman
\end{itemize*}
\secondarysectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Links}
Github:// \mbox{\href{https://github.com/abhijeetviswa}{\bf abhijeetviswa}}\\[3pt]
LinkedIn://  \mbox{\href{https://www.linkedin.com/in/abhijeetviswa}{\bf abhijeetviswa}} \\
\secondarysectionsep

% \section{Activities}
% \begin{tightemize}
% \item Member, \href{https://universe.bits-pilani.ac.in/Hyderabad/Computercentre}{Computer Center - IT}.
% \item Member, \href{https://github.com/io}{Crux} - the Programming and Computing Club.
% \item Member, English Language Activities Society, and Journal Club.
% \item Member, Wall Street Club.
% \end{tightemize}
% \sectionsep

\section{About Me}
\noindent \RaggedRight \normalfont
I am an engineering undergraduate passionate about Software Engineering, and started
programming at the age of 13. My current interests are Android app development and
backend web development. I am also actively involved with and passionate about Open Source.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage}
\hfill
\begin{minipage}[t]{0.70\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experience}
\runsubsection{Oracle}
\descript{| Incoming Summer Intern}
\location{May 2021- July 2021}
% Empty tightemize to negate effects
% of negative veritcal offset in next tightemize
\begin{tightemize}
\end{tightemize}
\subsectionsep

\runsubsection{Central Analytical Lab}
\descript{| Software Developer}
\location{January 2021 - Present}
\begin{tightemize}
 \item Maintainer of online portal of the Central Analytical Lab of BITS Pilani, Hyderabad.
 \item Portal made using Python and Django and services the Research Scholars.
\end{tightemize}
\subsectionsep

\runsubsection{\href{https://www.cuemath.com}{Cuemath}}
\descript{| Summer Intern}
\location{May 2020 – June 2020 | Bangalore, India}
\begin{tightemize}
\item Worked on creating Spatial Reasoning puzzles with the content creation team at Cuemath aimed at school children (6-12 years)
\item Worked on the backend of a web platform to crowd-source useful learning resources and materials related to any topics.
Backend was built using Django and Django REST Framework.
\end{tightemize}

\primarysectionsep  % end of section

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Projects and Open Source Contributions}
\runsubsection{CMS-Android}
\descript{| Open Source \href{https://moodle.org}{Moodle} Client for Android}
\location{May 2019 - Present | GitHub: {\href{https://github.com/crux-bphc/CMS-Android}{crux-bphc/CMS-Android}}}
\begin{tightemize}
\item Maintainer of the project.
\item Vital part of student academics, allows students to stay updated with announcements from professors.
\item 3000+ active users.
\end{tightemize}
\subsectionsep

\runsubsection{Moodle Extended Notifs}
\descript{| Plugin for adv push notifications}
\location{October 2020 - Present | GitHub: {\href{https://github.com/abhijeetviswa/moodle-local_extendednotifs}{abhijeetviswa/moodle\-local\_extendednotifs}}}
\begin{tightemize}
 \item A Moodle Plugin to send push notifications via Email and app when new modules and activities are created.
 \item Deployed to the \href{https://td.bits-hyderabad.ac.in}{Moodle instance} of BITS Pilani, Hyderbad Campus.
\end{tightemize}
\subsectionsep

\runsubsection{SmartCampus}
\descript{| A Mobile app for a Smarter Campus}
\location{September 2019 - Pres
ent}
\begin{tightemize}
 \item Built backend for SmartCampus, a mobile service to buy food inside campus.
 \item Used Django and Django REST Framework to built the web application, PostgreSQL for the database. Deployted to Digital Ocean
\end{tightemize}
\subsectionsep

\runsubsection{Django}
\descript{| Python Web Framework}
\location{January 2020 – Present | GitHub PRs: \href{https://github.com/django/django/pulls?q=author\%3Aabhijeetviswa}{django/django/pulls}}
\begin{tightemize}
\item \href{https://code.djangoproject.com/ticket/31246}{Reported} and \href{https://github.com/django/django/pull/12434}{fixed}
a release blocking bug related to concurrent select and update on tables.
\item \justifying\href{https://github.com/django/django/pull/12496}{Fixed} a bug related to redundant SQL queries being generated when
inserting a new row in a table.
\end{tightemize}
\primarysectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXTRA CURRICULLARS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \subsectionsep % Extra space for looks
% \section{Extra Curricular}
% \vspace{\itemsep}
% \begin{tightemize}
% \item Active student Member of \href{https://crux-bphc.github.io}{Crux - The Programming and Computing Club} of BITS Pilani, Hyderabad Campus.
% \end{tightemize}
\end{minipage}
\end{document}
