%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{resume}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Abhijeet}{Viswakumar}{
\faEnvelopeO\; \href{mailto:abhijeetviswa@gmail.com}{abhijeetviswa@gmail.com}
| \faGithub\; \href{https://github.com/abhijeetviswa}{abhijeetviswa}
| \faLinkedin\; \href{https://linkedin.com/in/abhijeetviswa}{abhijeetviswa}
| \faPhone\; +91 807 820 4438}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.25\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education}

\subsection{BITS Pilani}
\descript{B.E. Electronics and Instrumentation Engineering}
\location{July 2022 | Hyderabad, India}
\location{CGPA: \normalfont \textbf{8.29/10}}
\subsectionsep

\subsection{Amrita Vidyalayam}
\descript{CBSE Class XII, 95.8\%}
\location{March 2017 | Palakkad, India}
\subsectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{Coursework}
% \subsection{Graduate}
% Advanced Machine Learning \\
% Open Source Software Engineering \\
% Advanced Interactive Graphics \\
% Compilers + Practicum \\
% Cloud Computing \\
% Evolutionary Computation \\
% Defending Computer Networks \\
% Machine Learning \\
% \sectionsep
%
% \subsection{Undergraduate}
% Information Retrieval \\
% Operating Systems \\
% Artificial Intelligence + Practicum \\
% Functional Programming \\
% Computer Graphics + Practicum \\
% {\footnotesize \textit{\textbf{(Research Asst. \& Teaching Asst 2x) }}} \\
% Unix Tools and Scripting \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\itemlabel{Proficient}
\begin{itemize*}
 \item Python
 \item Java
 \item Kotlin
 \item C
 \item Bash
\end{itemize*}
\subsectionsep

\itemlabel{Familiar}
\begin{itemize*}
 \item SQL
 \item C++
 \item Typescript
\end{itemize*}
\subsectionsep

\subsection{AWS}
\begin{itemize*}
 \item Lambda
 \item DynamoDB
 \item ECS
 \item Fargate
 \item EC2
 \item CDK
\end{itemize*}
\subsectionsep

\subsection{Tools \& Technologies}
\begin{itemize*}
 \item Linux
 \item Django
 \item Android
 \item Docker
 \item REST
 \item Postman
\end{itemize*}
\secondarysectionsep

\section{About Me}
\noindent \RaggedRight \normalfont
I am a passionate software engineer with hands-on experience on backend and
infrastructure development on AWS. I'm also an Open Source enthusiast and
contributor.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage}
\hfill
\begin{minipage}[t]{0.70\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experience}

\runsubsection{Amazon Web Services (AWS)}
\descript{| Software Engineer}
\location{February 2022 - Present | Bangalore, India}
\vspace{2pt}
\location{Tech: Python, Typescript, EC2, Lambda, DynamoDB, Fargate}
\vspace{10pt}
\begin{tightemize}
\item  Created a service to automatically parse maintenance emails and suppress
relevant alarms. Resulted in reduced operational load and approx 5 fewer high
severity tickets weekly.
\item Reduced weekly effort spent on running manual and protacted regression tests by automating it.
This reduced the time spent on the test from 24 man-hours down to 8.
\item Worked on an easily deployable network virtualisation product that was integrated with
automated network config CI/CD and regression testing pipelines. Ultimately reduced cost by
replacing physical network labs.
\end{tightemize}
\subsectionsep

\runsubsection{Oracle}
\descript{| Software Engineering Intern}
\location{June 2021 - July 2021 | Bangalore, India}
\vspace{2pt}
\location{Tech: C, Oracle Solaris}
\vspace{1pt}
\begin{tightemize}
\item Improved performance and accessibility of historical data by adding support for
alternative data stores in the `vmstat` command for Oracle Solaris.
\item Worked on improving documentation and man pages for CLI tools.
\end{tightemize}
\subsectionsep  % end of section

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     OPEN SOURCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Open Source Contributions}
\runsubsection{Django}
\descript{| Python Web Framework}
\location{References:
	\href{https://github.com/django/django/pulls?q=author\%3Aabhijeetviswa+state\%3Amerged}{GitHub PRs}}
\vspace{2pt}
\location{Tech: Python, Django}
\vspace{1pt}
\begin{tightemize}
\item \href{https://code.djangoproject.com/ticket/31246}{Reported} and \href{https://github.com/django/django/pull/12434}{fixed}
a release blocking bug related to concurrent select and update on tables. This fixed a previously undiscovered data corrupting bug.
\item \justifying\href{https://github.com/django/django/pull/12496}{Fixed} a bug related to redundant SQL queries being generated.
This improved database performance when inserting new rows into tables.
\item \justifying \href{https://github.com/django/django/pulls?q=author\%3Aabhijeetviswa}{Improved} Django codebase and documentation.
\end{tightemize}
\subsectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Projects}
\runsubsection{SmartCampus}
\descript{| A Mobile app for a Smarter Campus}
\location{References: \href{https://play.google.com/store/apps/details?id=com.smartcampus\_bphc}{Play Store}}
\vspace{2pt}
\location{Tech: Django, PostgreSQL REST, DigitalOcean}
\vspace{2pt}
\begin{tightemize}
 \item Designed and built the backend for SmartCampus, a mobile service to order food from one's hostel room.
 \item 4000+ active student users placed orders and were notified for order pick-up.
 \item Gross transaction value over a year (2 semesters) was Rs 3.1 crore.
\end{tightemize}
\subsectionsep

\runsubsection{CMS-Android}
\descript{| Open Source Moodle Client for Android}
\location{References: |
	\href{https://github.com/crux-bphc/CMS-Android}{GitHub} \& \href{https://play.google.com/store/apps/details?id=crux.bphc.cms}{Play Store}}
\vspace{2pt}
\textbf{Tech:} Android, Java, Kotlin
\vspace{2pt}
\begin{tightemize}
\item Developed and maintained a 3rd Party Moodle client.
\item Allows students to enrol to courses, access, be notified, and provided offline access to courses contents
on their phone.
\item Vital part of academic life with 4000+ active student users.
\end{tightemize}
\subsectionsep
\primarysectionsep  % end of section

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXTRA CURRICULLARS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \subsectionsep % Extra space for looks
% \section{Extra Curricular}
% \vspace{\itemsep}
% \begin{tightemize}
% \end{tightemize}

%%%%%%%%%%%%%%%%
%    THE END
%%%%%%%%%%%%%%%%
 \end{minipage}
 \end{document}

